Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Validated Saturn-Sized Planet in IC~2602

### 2020-07-14 paper/ms.tex
update manuscript

%
% TODO:
% * Zhou or Quinn: what is the SpType? Add to abstract, tables, and
% text. G0/F9V has been assumed.
% * remove all bf todo's
%

@@

Finding and studying systems undergoing these evolutionary changes is
a major goal in contemporary exoplanet research.  To identify stars
younger than say 1$\,$Gyr, a number of direct and indirect methods are
available \citep{soderblom_ages_2010}.  The traditional approach is to
isochronally age-date coeval groups of stars, hereafter ``clusters''
\citep[{\it
e.g.},][]{lada_embedded_2003,zuckerman_young_2004,krumholz_star_2019}.
Young field stars can also be identified
isochronally, provided that they are sufficiently massive \citep{berger_gaia-kepler_2020}. 
Other age indicators include
stellar rotation periods, the abundance of photospheric lithium, and
chromospheric diagnostics such as calcium emission and broadband UV
emission.  Studies by for instance \citet{david_discovery_2018} and
G{.}~Zhou et al. (2020, submitted) have combined these methods to age-date
individual field stars hosting transiting planets.  Many of these latter methods were summarized by
\citet{mamajek_improved_2008}, and have since been calibrated by {\it
e.g.},
\citet{irwin_rotational_2009,barnes_color-period_2015,meibom_spin-down_2015,angus_calibrating_2015}
and \citet{curtis_tess_2019} for stellar rotation,
\citet{zerjal_chromospherically_2017} for chromospheric activity, and
{\it e.g.}, \citet{elliott_search_2016,berger_identifying_2018} and
\citet{zerjal_galah_2019} for lithium abundances.

@@

Section~\ref{sec:observations} describes the identification of the
candidate, and the follow-up observations collected.
Section~\ref{sec:validation} combines these data to assess the
system's false positive probability, and validates \pn\ as a planet.
Section~\ref{sec:system} presents our knowledge of the cluster
(Section~\ref{subsec:cluster}), the star (Section~\ref{subsec:star})
and the planet (Section~\ref{subsec:planet}).  We conclude by
discussing avenues for confirmation and improved characterization in
Section~\ref{sec:discussion}.

@@

The above exercise ruled out the possibility that the observed
eclipses are caused by a stellar-mass object orbiting \tn.  The lack
of a linear trend in the radial velocities, particularly in the FEROS
data, further constrains the presence of a hierarchical binary system.
To derive limits for this second possibility, we placed a wide
log-uniform prior on the semi-amplitude and period ($\log K\ [{\rm
m\,s^{-1}}] \sim \mathcal{U}(1,10^5)$, $\log P\ [{\rm days}] \sim
\mathcal{U}(0.1, 10^{15})$).  We then fitted for the semi-amplitude,
period, time of conjunction, instrument offsets, and jitter
parameters.  We converted the resulting posterior in period and
semi-amplitude to minimum mass and semi-major axis assuming Kepler's
third law.  The resulting $3\sigma$ limits are shown in
Figure~\ref{fig:fpscenario}.

@@

%\clearpage
\acknowledgements
\raggedbottom

@@

>>>>

%
% TODO:
% * remove all bf todo's
%

@@

Finding and studying systems undergoing these evolutionary changes is
a major goal in contemporary exoplanet research.  To identify stars
younger than say 1$\,$Gyr, a number of direct and indirect methods are
available \citep{soderblom_ages_2010}.  The traditional approach is to
isochronally age-date coeval groups of stars, hereafter ``clusters''
\citep[{\it
e.g.},][]{lada_embedded_2003,zuckerman_young_2004,krumholz_star_2019}.
Young field stars can also be identified
isochronally, provided that they are sufficiently massive \citep{berger_gaia-kepler_2020}. 
Other age indicators include
stellar rotation periods, the abundance of photospheric lithium, and
chromospheric diagnostics such as calcium emission and broadband UV
emission.  Studies by for instance \citet{david_discovery_2018} and
G{.}~Zhou et al{.}~(2020, submitted) have combined these methods to age-date
individual field stars hosting transiting planets.  Many of these latter methods were summarized by
\citet{mamajek_improved_2008}, and have since been calibrated by {\it
e.g.},
\citet{irwin_rotational_2009,barnes_color-period_2015,meibom_spin-down_2015,angus_calibrating_2015}
and \citet{curtis_tess_2019} for stellar rotation,
\citet{zerjal_chromospherically_2017} for chromospheric activity, and
{\it e.g.}, \citet{elliott_search_2016,berger_identifying_2018} and
\citet{zerjal_galah_2019} for lithium abundances.

@@

Section~\ref{sec:observations} describes the identification of the
candidate, and our follow-up observations.
Section~\ref{sec:validation} combines the available data to assess the
system's false positive probability, and validates \pn\ as a planet.
Section~\ref{sec:system} presents our knowledge of the cluster
(Section~\ref{subsec:cluster}), the star (Section~\ref{subsec:star})
and the planet (Section~\ref{subsec:planet}).  We conclude by
discussing avenues for confirmation and improved characterization in
Section~\ref{sec:discussion}.

@@

The above exercise ruled out the possibility that the observed
eclipses are caused by a stellar-mass object orbiting \tn.  The lack
of a linear trend in the radial velocities, particularly in the FEROS
data, further constrains the presence of a hierarchical binary system.
To derive limits for this second possibility, we placed a wide
log-uniform prior on the semi-amplitude and period ($\log K\ [{\rm
m\,s^{-1}}] \sim \mathcal{U}(1,10^5)$, $\log P\ [{\rm days}] \sim
\mathcal{U}(0.1, 10^{15})$).  We then fitted for the semi-amplitude,
period, time of conjunction, instrument offsets, and jitter
parameters.  We converted the resulting posterior in period and
semi-amplitude to minimum mass and semi-major axis assuming Kepler's
third law.  The resulting $3\sigma$ limits are shown in
Figure~\ref{fig:fpscenario}.
{\it LGB TODO: the procedure in the preceding paragraph might be modified to
	instead convert the FEROS limit $|\dot{\gamma}| < 0.82\,{\rm m\,s}^{-1}\,{\rm
		day}^{-1}$ directly into a semi-amplitude limit.}

@@

%\clearpage
\acknowledgements
%\raggedbottom

@@

Resources supporting this work were provided by the NASA High-End
Computing (HEC) Program through the NASA Advanced Supercomputing (NAS)
Division at Ames Research Center for the production of the SPOC data
products.
